Active Learning from Blackbox to Timed Connectors

### 2016-01-11 paper/paper.tex
.

@@

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% listing for codes
\usepackage{listings}
% listing for golang
% NOTE listings-golang.sty is required
\usepackage{listings-golang}

% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

@@

\begin{IEEEkeywords}
  Active Learning, Coordination Languages, Formal Methods
\end{IEEEkeywords}

@@

\todo{a figure illustrating the framework of active learning}

Figure shows a sketch of active learning, wherein
\begin{itemize}
  \item[-]
\end{itemize}

>>>>

\usepackage{graphicx}

@@

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% listing for codes
\usepackage{listings}
% listing for golang
% NOTE listings-golang.sty is required
\usepackage{listings-golang}
% to support flow graphs
\usepackage{textcomp}

% positioning is used for below lef = of
\usetikzlibrary{shapes,shadows,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

@@

\begin{IEEEkeywords}
  Active Learning, Coordination Languages, Timed Connectors
\end{IEEEkeywords}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.4\textwidth]{./images/activelearning.png}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

Figure \ref{fig:activelearning} shows a sketch of active learning, wherein:
\begin{itemize}
  \item[-]
\end{itemize}
